---
title: "Presentation"
author: "Anthony James"
date: "March 4, 2016"
output: ioslides_presentation
---

output: ioslides_presentation
output: beamer_presentation  (slides on the left)

output: html

htmlwidgets in r
htmlwidgets.org
Showcase



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

c->
```{r }
library(dygraphs)
dygraph(nhtemp, main = "New Haven Temperatures") %>% 
  dyRangeSelector(dateWindow = c("1920-01-01", "1960-01-01"))

```

---
use hypthens to spearate slides

---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

